```{r}
library(tidyverse)
library(tidymodels)
library(GGally)
library(lmtest)
```

```{r}
air = airquality
```

```{r}
str(air)
```
```{r}
air2 = air %>% drop_na()
```

```{r}
ggpairs(air2)
```
```{r}
ggcorr(air2,label="TRUE")
```
```{r}
ggplot(air2, aes(x=Temp,y=Ozone)) + geom_point() + 
  geom_smooth(method="lm",se=FALSE, color="red") + theme_bw()
```
```{r}
#reusing code from before (just changing names where needed)
air2_simple = recipe(Ozone ~ Temp, air2)

lm_model = #give the model type a name 
  linear_reg() %>% #specify that we are doing linear regression
  set_engine("lm") #specify the specify type of linear tool we want to use 

lm_wflow = 
  workflow() %>% 
  add_model(lm_model) %>% 
  add_recipe(air2_simple)

lm_fit = fit(lm_wflow, air2)
```
```{r}
summary(lm_fit$fit$fit$fit)
```
```{r}
confint(lm_fit$fit$fit$fit)
```

```{r}
testdata = data.frame(Temp = c(80))
predict(lm_fit, new_data = testdata)
```
**Assumption 1:** The predictor and response variable have a linear relationship  
As noted above, it seems "reasonable" to say that there is something of a linear relationship between these two variables, but there is definitely a nonlinear effect present.  

**Assumption 2:** Model errors (residuals) are independent  
Let's use the Durbin-Watson Test to examine independence of residuals. The dwtest function is from the lmtest package.  
```{r}
dwtest(lm_fit$fit$fit$fit)
```
We fail to reject the null hypothesis with a p-value greater than 0.05. This suggests that the residuals are likely independent.  

**Assumption 3:** Model residuals exhibit constant variance  
Examine a plot of residuals.  
```{r}
air2 = air2 %>% mutate(resid1 = lm_fit$fit$fit$fit$residuals) #add the model residuals to our data frame
ggplot(air2,aes(x=Temp,y=resid1)) + geom_point() + theme_bw()
```
A non-linear effect is present.

**Assumption 4:** Model residuals are Normally-distributed  
Examine a histogram of the residuals.  
```{r}
ggplot(air2,aes(x=resid1)) + geom_histogram() + theme_bw()
```

